\Title

### 2021-01-26 manuscript/manuscript.tex
Merge the gradient boosting results into 1 figure
Easier to compare and the figures share x and y axis so this fits
nicely.

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

We have also registered the computational time needed to fit the
gradient-boosted equivalent sources for each window size and computed the ratio
between these times and the computational time needed to fit the non-boosted
equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against window size.
        Window sizes are given as a fraction of the dimensions of the synthetic
        survey area.
        (a)~Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different window sizes. Each RMS
        error is the mean of the RMS produced by the same set of parameters but
        with different random seeds.
        (b)~Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
}
    \label{fig:gradient-boosted-window-size}
\end{figure}

@@

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against amount of
        overlap.
        (a)~Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different amount of overlap. Each
        RMS error is the mean of the RMS produced by the same set of parameters
        but with different random seeds.
        (b)~Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
    }
    \label{fig:gradient-boosted-overlap}
\end{figure}

@@

>>>>

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients (see Fig.~\ref{fig:gradient-boosted-comparison}a).
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

We have also registered the computational time needed to fit the
gradient-boosted equivalent sources for each window size and computed the ratio
between these times and the computational time needed to fit the non-boosted
equivalent sources (see Fig.~\ref{fig:gradient-boosted-comparison}b).

@@

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-comparison}d).

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Comparison of the interpolation RMS error and computation time for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Both methods used the same source positions (block-averaged sources
        with a relative depth).
        Window sizes are given as a fraction of the survey area (e.g., 1
        represents a window with the same area as the survey) and window
        overlap is given as a fraction of the window size (e.g., 0.5 equals
        50\% overlap).
        Computation time refers to the time required to estimate the source
        coefficients and is reported as a ratio between the gradient-boosted
        and the regular equivalent sources.
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars represent 1 standard deviation) of results using
        different seeds for the pseudo-random number generator.
        (a)~RMS error between the target grid and interpolation results and
        (b)~computation time as a function of window size.
        (c)~RMS error between the target grid and interpolation results and
        (d)~computation time as a function of window overlap.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}
